### 2023-12-10 Paper Writeup/main.tex
Github repo link added
FInal changes made to the paper

% This command causes the title to be created in the document
\newpage
\section{Abstract}

@@

Originating in the 1970s, the utilization of the Normalized Difference Vegetation Index (NDVI) has undergone a transformative evolution. Initially designed for vegetation detection, it has progressed to become an invaluable tool for monitoring and predicting vegetation health and growth. This comprehensive methodology has found substantial application in environmental monitoring, notably in the Brazilian forest [3]. Employing the Random Forest model, historical NDVI data has been meticulously analyzed to not only comprehend the past growth patterns of the Brazilian forest but also to project future developments. Using the GEEE platforms to extract the utilize the data available, the data was then processed and checked against the Random Forest algorithm to monitor the changes over the years, and see the future vegetation prospects based on this idea.

The versatility of NDVI extends to pattern monitoring, exemplified by the Mimbo forests [4]. In this context, the NDVI method served as a robust metric for quantifying deforestation. Incorporating regression analysis into the evaluation of identified patterns has not only facilitated a nuanced understanding of past deforestation trends but also augments the capability to predict future vegetation dynamics within the Mimbo region.

@@

% We also used parameters like timing the execution or running time of our programs to see which program runs faster. 
\section{Implementation}
\subsection{Image Clustering}
Our code implements the Fuzzy C-Means (FCM) clustering algorithm for image segmentation, focusing on feature detection, especially in identifying vegetation. We start by initializing a membership matrix, a crucial part of FCM, where each entry signifies the pixel's association degree with each cluster, capturing the uncertainty in pixel assignments during clustering. The iterative refinement of cluster centers and the membership matrix is then executed through a structured process.

@@

\section{Experimental Results}
Each of our code were executed and timed appropiately. Where analysis was done not by only varying the parameter values but also working principle of each code with varying image types and the type of landscape provided to it as well. Each method would be discussed and the type of result that it had provided with.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{fig1a.PNG} % Replace 'image1' with your actual filename
        \caption{Caption for Figure 1a}
        \label{fig:subfig1}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{fig1b.PNG} % Replace 'image2' with your actual filename
        \caption{Caption for Figure 1b}
        \label{fig:subfig2}
    \end{subfigure}
    \caption{Overall caption for both figures.}
    \label{fig:overall}
\end{figure}

@@

It is observable based on the table 1 above where the time taken for each NDVI and Clustering is almost equal, clustering would still be giving an estimate as compared to the NDVI method. However based on the technique and idea used to get information and the idea of automation, clustering would give a good estimate while having the idea of getting incorporated with automation tasks which involve only taking the screen shot of the map as compared to NDVI where automation would also be complicated as the selected files would have to contain the required bands. Thus, both the ideas could also be used to track forestation as seen in fig 4 where the red area identifies the area of deforestation and blue identifies the area of afforestation. Where with some additional changes, it could further be improved to the extent where the area of deforestation and afforestation could also be found.

@@

@@

\section{Conclusion}

@@

Citations for NDVI and intext too. Also, cite the 3rd paper and others
\end{document}

>>>>

% This command causes the title to be created in the document
\newpage
\section{Abstract}
Satellite imagery stands as a pivotal tool, progressively evolving to provide insightful information and monitor various topological transformations. Despite its substantial capabilities, there is an underutilization due to a lack of guidance on effective tool utilization. This research addresses this gap by offering insights into selecting suitable platforms and providing essential information about the monitored area, facilitating efficient tracking of deforestation or afforestation. Instead of relying on the complex and data-intensive Normalized Difference Vegetation Index (NDVI) method, this study adopts a pragmatic approach using clustering methods.

Through experimentation, even with a simple screenshot of the targeted area, the proposed method yields accurate approximations, proving effective in tracking deforestation activities. This research establishes a streamlined and accessible methodology for monitoring environmental changes, fostering sustainable practices through a straightforward and reliable clustering approach.

@@

Originating in the 1970s, the utilization of the Normalized Difference Vegetation Index (NDVI) has undergone a transformative evolution. Initially designed for vegetation detection, it has progressed to become an invaluable tool for monitoring and predicting vegetation health and growth. This comprehensive methodology has found substantial application in environmental monitoring, notably in the Brazilian forest \cite{su11010098}. Employing the Random Forest model, historical NDVI data has been meticulously analyzed to not only comprehend the past growth patterns of the Brazilian forest but also to project future developments. Using the GEEE platforms to extract the utilize the data available, the data was then processed and checked against the Random Forest algorithm to monitor the changes over the years, and see the future vegetation prospects based on this idea.

The versatility of NDVI extends to pattern monitoring, exemplified by the Mimbo forests \cite{ijgi9100580}. In this context, the NDVI method served as a robust metric for quantifying deforestation. Incorporating regression analysis into the evaluation of identified patterns has not only facilitated a nuanced understanding of past deforestation trends but also augments the capability to predict future vegetation dynamics within the Mimbo region.

@@

% We also used parameters like timing the execution or running time of our programs to see which program runs faster. 
\section{Implementation}
The implementation of the sections discussed below can be found on our Github repository \cite{adip_group_project}
\subsection{Image Clustering}
Our code implements the Fuzzy C-Means (FCM) clustering algorithm for image segmentation, focusing on feature detection, especially in identifying vegetation. We start by initializing a membership matrix, a crucial part of FCM, where each entry signifies the pixel's association degree with each cluster, capturing the uncertainty in pixel assignments during clustering. The iterative refinement of cluster centers and the membership matrix is then executed through a structured process.

@@

\section{Experimental Results}
We used the methods and implemented them on the images of Punhal Khan Jamali, Each of our code were executed and timed appropiately. Where analysis was done not by only varying the parameter values but also working principle of each code with varying image types and the type of landscape provided to it as well. Each method would be discussed and the type of result that it had provided with.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{fig1a.PNG} % Replace 'image1' with your actual filename
        \caption{Figure 1a.1: For 6 number of clusters}
        \label{fig:subfig1}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{fig1a_ans.PNG} % Replace 'image2' with your actual filename
        \caption{Figure 1a.2: Impact on the real image}
        \label{fig:subfig2}
    \end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{fig1b.PNG} % Replace 'image1' with your actual filename
        \caption{Figure 1b.1: For 3 number of clusters}
        \label{fig:subfig3}
    \end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{fig1b_ans.PNG} % Replace 'image1' with your actual filename
        \caption{Figure 1b.2: Impact on the real image}
        \label{fig:subfig4}
    \end{subfigure}
    \caption{Changing the number of clusters in FCM}
    \label{fig:overall}
\end{figure}

@@

It is observable based on the table 1 above where the time taken for each NDVI and Clustering is almost equal, clustering would still be giving an estimate as compared to the NDVI method. However based on the technique and idea used to get information and the idea of automation, clustering would give a good estimate while having the idea of getting incorporated with automation tasks which involve only taking the screen shot of the map as compared to NDVI where automation would also be complicated as the selected files would have to contain the required bands. Thus, both the ideas could also be used to track forestation as seen in Figure 3 where the red area identifies the area of deforestation and blue identifies the area of afforestation. Where with some additional changes, it could further be improved to the extent where the area of deforestation and afforestation could also be found.

@@

% add system specifications on which the results are run
\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{fig2a.jpg} % Replace 'image1' with your actual filename
        \caption{Deforested area}
        \label{fig:subfig1}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{fig2red.jpeg} % Replace 'image2' with your actual filename
        \caption{Amount of vegetation detected}
        \label{fig:subfig2}
    \end{subfigure}
    \caption{Blur image being used}
    \label{fig:overall}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth, height=6cm]{Figure 3.jpg} % Replace 'your_image_filename' with the actual filename of your image
    \caption{afforestation: Blue, deforestation: Red}
    \label{fig:your_label}
\end{figure}

@@

\section{Conclusion}
Upon analyzing the outcomes derived from each experimental result, we can confidently assert the efficacy of Fuzzy C-Means (FCM) as a robust method for vegetation identification within a given area. Notably, this approach stands out due to its versatility in accommodating diverse image formats such as JPEG, TIFF, PNG, and others, setting it apart from methods like Normalized Difference Vegetation Index (NDVI) that necessitate images from each band. Our comprehensive examination leads us to conclude that FCM clustering serves as a compelling alternative, offering valuable insights into the extent of forestation. This approach eliminates the need for intricate satellite selection and the handling of large data files associated with extremely high-resolution band-specific images. The simplicity and accuracy of FCM make it a practical choice for assessing vegetation cover in diverse environmental contexts. However, there are limitations to this approach, firstly being the less accurate dataset as we use Google Earth images instead of the multi-band satellite images that are dedicated to the identfication of the topology and Earth's natural resources. Secondly, we could not come up with a way of quantfying the accuracy of the classical methods with the NDVI method which uses multi-band imagery, and thus a quantitative comparison becomes virtually impossible.

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.40\textwidth}
        \includegraphics[width=\linewidth, height=4.5cm]{ex1_cluster.PNG} % Replace 'image1' with your actual filename
        % \caption{Caption for Figure 1a}
        \label{fig:subfig1}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.40\textwidth}
        \includegraphics[width=\linewidth, height=4.5cm]{ex1_NDVI.PNG} % Replace 'image2' with your actual filename
        % \caption{Amount of vegetation detected}
        \label{fig:subfig2}
    \end{subfigure}
	\hfill
    \begin{subfigure}{0.40\textwidth}
        \includegraphics[width=\linewidth, height=4.5cm]{ex1_sat.PNG} % Replace 'image2' with your actual filename
        %  \caption{Amount of vegetation detected}
        \label{fig:subfig2}
    \end{subfigure}
	\hfill
    \begin{subfigure}{0.40\textwidth}
        \includegraphics[width=\linewidth, height=4.5cm]{example1.PNG} % Replace 'image2' with your actual filename
        % \caption{Amount of vegetation detected}
        \label{fig:subfig2}
    \end{subfigure}
    \caption{Vegetation detected using different methods}

    \label{fig:overall}
\end{figure}

@@

% Citations for NDVI and intext too. Also, cite the 3rd paper and others
\end{document}
